### 2011-04-24 docs/architecture/architecture.tex
more boxlib descriptions

\MarginPar{Nesting?}
For parallel computations, the boxes are spread across processors, in
a fashion designed to put roughly equal amounts of work on each
processor (load balancing).

@@

For a \boxtype\ declared as:
\begin{verbatim}
  type(box) :: mybox
\end{verbatim}

@@

A \fab\ is a ``Fortran Array Box''.  It contains the state data in a
multidimensional array and several \boxtype-types to describe where in
index-space it lives.  The datatype of a \fab\ is
\begin{verbatim}
  type fab
     integer   :: dim = 0
     type(box) :: bx
     type(box) :: pbx
     type(box) :: ibx
     integer   :: nc = 1
     real(kind = dp_t), pointer, dimension(:,:,:,:) :: p => Null()
  end type fab
\end{verbatim}

\noindent Here:
\begin{itemize}
\item {\tt dim} is the dimensionality of the data
\item {\tt bx} is a \boxtype\ describing the index space for which this \fab\ is defined
\item {\tt ibx} is a \boxtype\ that describes the index range of the valid data
  for the \fab.  This differes from {\tt bx} when the box is nodal in one or more 
  directions.
\item {\tt pbx} is a \boxtype\ that extends {\tt ibx} to include
  any ghostcells, or equivalently, the physical box for the \fab\
\item {\tt nc} is the number of components (how many variables at  
  each grid location)
\item {\tt p} is a pointer to the data, in this case double precision
  ({\tt kind=dp\_t}).  Other \fab\ types exists for other Fortran
  data types.
\end{itemize}

Note that all state data is stored in a four-dimensional array,
{\tt (nx,ny,nz,nc)} in size, regardless of the dimensionality of the
problem.  For 2D problems, {\tt nz=1}.

In MAESTRO, we don't usually deal with \fab s alone, but rather
through \multifab s, described next.

A \multifab\ is a collection of \fab s at the same level of
refinement.  The data type of a \multifab\ is:
\begin{verbatim}
  type multifab
     integer :: dim = 0
     integer :: nboxes = 0
     integer :: nc = 1
     integer :: ng = 0
     logical, pointer :: nodal(:) => Null()
     type(layout) :: la
     type(fab), pointer :: fbs(:) => Null()
  end type multifab
\end{verbatim}

@@

@@

>>>>

\MarginPar{Nesting? ghost cells?}
For parallel computations, the boxes are spread across processors, in
a fashion designed to put roughly equal amounts of work on each
processor (load balancing).

@@

A \boxtype\ declared as:
\begin{verbatim}
  type(box) :: mybox
\end{verbatim}
%
The upper and lower bounds of the box (in terms of the global
index space) are found via:
\begin{itemize}

@@

@@

A \fab\ is a ``Fortran Array Box''.  It contains the state data in a
multidimensional array and several \boxtype-types to describe where in
the global index-space it lives.  
Note that all state data is stored in a four-dimensional array,
{\tt (nx,ny,nz,nc)} in size, regardless of the dimensionality of the
problem.  Here {\tt nc} is the number of components, for instance
representing different fluid variables.  For 2D problems, {\tt nz=1}.

A \fab\ would represent the data for a single box in the domain.
In MAESTRO, we don't usually deal with \fab s alone, but rather
we deal with \multifab s, described next.

A \multifab\ is a collection of \fab s at the same level of
refinement.  This is the primary data structure that MAESTRO
routine operate on.  A multilevel simulation stores the 
data in an array of multifabs, where the array index refers
to the refinement level.

\subsubsection{Working with \multifab s}

To build a \multifab, we need to provide a \layout, the number of
components to store in the multifab, and the number of ghostcells.  In
MAESTRO, the hierarchry of grids will be described by a single
\mllayout.  A \multifab\ can be declared and built at any time in a
simulation using the \mllayout, thereby allocating space at every
grid location in the simulation.  The sequence to build a \multifab\
appears as
\begin{verbatim}
  type(multifab) :: mfab(nlevs)
  ...
  do n = 1, nlevs
     call multifab_build(mfab(n), mla%la(n), nc, ng)
  enddo
\end{verbatim}
Here, {\tt nc} is the number of components and {\tt ng} is the number
of ghostcells.  The \multifab\ is built one level at a time, using the
\layout\ for that level taken from the \mllayout, {\tt mla}.

A common operation on a \multifab\ is to initialize it to $0$
everywhere.  This can be done (level-by-level) as
\begin{verbatim}
call setval(mfab(n), ZERO, all=.true.)
\end{verbatim}
where {\tt ZERO} is the constant 0.0 from {\tt bl\_constants\_module}.

Subroutines to add, multiply, or divide two \multifab s exist, as do
subroutines to copy from one \multifab\ to another---see {\tt boxlib/multifab.f90}
for the full list of routines that work with \multifab s.

When you are done working with a \multifab, its memory can be freed by
calling {\tt multifab\_destroy} on the \multifab.

@@

A \bctower holds the information about what boundary conditions are
in effect for each variable in a MAESTRO simulation.  \MarginPar{better description?}
